\documentclass[letterpaper]{article}

% Enable the use of graphics and color typesetting
\usepackage{graphicx,color}
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage[T1]{fontenc} %Required to use Times New Roman fonts
\usepackage{parskip}
\renewcommand{\rmdefault}{ptm}

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1} % Line spacing

\setlength\parindent{0pt} % Removes all indentation from paragraphs

\begin{document}

\title{Advanced Squad Leader Slang and Jargon Glossary v1.11}
\author{Glenn Connot}

\maketitle

\newpage

\tableofcontents

\newpage

\section{Disclaimer}

All terms were taken from ASLML posters; credit is given to terms whose origin
is known, not necessarily the person who posted it (who is not credited). Most
terms are reproduced verbatim; some were edited for formatting, spelling, or
simple grammar. Any mistakes in reproduction are mine.

Using any term in any way requires a royalty fee, which can be mailed to the compiler who will make sure that a percentage of the fee is sent along to the original submitter, unless I forget or just don't feel like it in which case I'll keep it all.


\section{A}

Aaahhh!  Bright Light!: Starshells/IRs, a la Gremlins... must be in high-pitch tone.

Aamco Check: The Mechanical Reliability DR for an AFV.

Acqued-up: Acquired unit/Location/hex.

Acquisition Shot: A TH attempt with only an Improbable chance to hit; usually said of AFV AFPh MA shots.

Agonizing reappraisal of the whole scene: Time to rethink your strategy. From "Fear and Loathing in Las Vegas".

Air Strike: Air support

Alamo: Any building hex where the defender makes a last stand. From "Saving Private Ryan", and also the event itself.

All-weather Smoke: Armor likely to end the scenario as a Burning Wreck. See also Russian Smoke.

Alternate Reality: Dropping the dice for some choice you decided not to take, just to see what the results might have been.

... And looked good doing it! : An addition to the end of a declaration of success when you roll 2 or 3 for a check, when a much higher number would have been sufficient, and there is no benefit beyond success. Ex: Rolling snakes on an ESB or Radio Contact check.

All-important wind DR: We've rolled thousands and had two wind changes in 15 years.

A lot of sound and fury, signifying nothing: An attack with great potential that whimpers because of bad dice. Bastardization of Macbeth's soliloquy, "It is a tale told by an idiot, full of sound and fury, signifying nothing"

Amis: Americans.

Amoeba: A large multi-hex FG, usually used in the desert, where you have a FG of 6-8 squads in separate hexes. Or, a large, multi-hex fire group, no/few units stacked. See also Blob.

Amoving: Assault Moving (from VASL log files, rarely said in person).

Anal-retentive b*st*rd: Someone who insists on following ALL the rules to the letter, and never allows or asks for an exception.

Anyone Home?: Asked when Searching or simply moving into an enemy unit's location, the latter also being known as "bump-scouting", since if there is an enemy unit there, the scouting unit is bumped back into his previous location.

Arnold: A 10-3 leader.

Arsonist: FT toting engineer.

ASLOK: Advanced Squad Leader OKtoberfest.

Asphalt Move: Assault move, especially one onto a paved road hex.

Assault Limp:  Wounded Leader movement.

Assume the position: The act of looking up a rule during play. ("Assume the position" usually means something very different to me, but it's equally applicable to my ASL game. -Chris von Seggern)

A2: Referring to rule A.2, which states in part "All results stand once play has progressed past the point of commission." Essentially, covering up one's mistakes in one's favor by jokingly disallowing the opponent from asking the mistake to be fixed.

Average Luck: A DR of `7' (and no ROF).

\section{B}

Baby, Baby Sniper: Sniper roll of a 2 instead of a 1.

Bag Man: Unit possessing a DC.

Bahamut: 1) An AFV immune to nearly everything you have to throw at it. 2) A unit, stack, or OoB that has progressed beyond your ability to cope with it (esp. in CGs, which can turn sour with one bad CG Day.)

Bailin' hay: An effective CC/Melee or a unit that succeeds in CC/Melee more than once.  Works better in Up Front but does apply to ASL, too.

Bait: 1) A valuable SW that was dropped in a vulnerable position, just screaming to be recovered. May become a Meat Grinder Hex or Hex of Death. 2) Any unit used to draw fire from the opponent so that more valuable units won't get hit (HS's vs. HIPped killstacks, halftracks vs. AT guns, etc)

Baldrick: A "cunning plan" that never works or that goes spectacularly wrong.

Barrio, the: Board 1

Barn: A double-large tank.  Derived from the incredible ease with

which other units can hit it, and the humor when a unit fails to.

Barry Sanders: An SMC DC carrier.

Bat: Plane making a Mistaken Air Attack

Battlefield Legal Name Change: Battle hardening or degrading of a Leader. (They magically acquire a new name).

Battle Hard-on:  As in, "my squad battle-hard-ons to a 6-6-7."

Battle Taxi: Armored Halftrack.

BAZ, Baz: Bazooka.

Bean Counter:  IIFT user.

Beasty, Beasties: U.S. 1st Line 6-6-6 squad/s.

Beckered: As in B E CR'ed.  Roll a 12 during a morale check and you're Broken, ELR'ed and Casualty Reduced.

Beehive: Canister

Behemoth: A tank that is significantly more powerful and larger than any other tanks in the scenario. (Depending on date, it might be a KV, Tiger, Elefant, etc.)

Belcher: To lose, you lost (ASL Name Slang)

Belford: To rant on MMP (ASL Name Slang)

Belt-fed: A Gun with a good ROF, either by design or good dice rolls.

Benched: Heroic Leader kept away from fire to man a Rally point

Bengal (may change to Lion this year):  Any very poor unit.  Shouldn't be in the game really.

Beauty Cat: Russian SU-85.

Blind: A unit that has no LOS or very high TEM to enemy units.

Blink Tank (copyright Tim Hundsdorfer): A tank that magically teleports to a
new hex after you pick up the counter to look at the back

BLOAT (Copyright Sam Belcher): Stands for "Biggest Loser of All Time". AKA Sam Belcher. Antithesis of Grofaz.

Blob: A large multi-hex FG, usually used in the desert, where you have a FG of 6-8 squads in separate hexes. Or, a large, multi-hex firegroup, no/few units stacked. See also Amoeba.

Blue: DM

Blue Badge of Courage, the: DM'ed.

Blue Badge of Cowardice, the: DM'ed.

Blutarski: A totally stupid action that works beyond your wildest imagination.

Board Edge Creep, Edge Creep: Attacking down a board edge, being able to disregard the off board flank. (Sometimes backfires when your brokies attempt to rout)

Board flip:  When someone gets really pissed off.

Bold Move: A move likely to draw/force effective fire. Alternately, an assault move through deep cover, far from enemy fire.

Bones: Dice

Boogerflicker: A gun that won't do much to the tanks it's facing. (37L ATGs)

Bounced: 1) A non-Dud AP hit that fails to effect armor. 2) Infantry prevented, by the presence of an enemy unit, from entering a hex.

Boxcars: Rolling 6's on both six-sided dice.

Brave, Brave Sir Robin:  A leader who fails a NMC. (Monty Pythonism)

Breaking Wind: Rolling a 12 on wind change.

Bring up the holy hand grenade!: Time to lay a DC. (Monty Pythonism)

"Bring that weak stuff, Meat": (Line from the movie 'Bull Durham') Said when facing huge firepower. Like a 10-3, HMG, 658 stack.

Broke their Rifles: A DR of 6,6 on an inherent firepower attack.

Brokie: A broken unit

Brush Off: Forcing Bailout of AFV Riders via TCA change, entering Orchard, etc.

Bullet magnet: A unit used to draw fire. Also known as Rhodes Scholars or Volunteers.

Bullet soup special: Rolling snake eyes.

Bullet sponge: A unit used to draw fire.

Bump and Butt: A `bounce' move to strip a ?, followed by the Assault Move of a friendly ? unit, Adjacent to that stripped unit.

Bump-scouting: Moving into a Concealed or HIP enemy unit's location.

Bush (the): Woods hexes

Buzz Lightyear Moment (copyright Tom Repetti): My understanding of the term is "a deft application of an obscure or seldom-used rule that provokes admiration from your opponent, but results in an adverse effect on your unit(s)," but I'll defer to Tom for a more precise definition. (From Repetti): I'd say Buzz Lightyear ASL is generally the unintentional pursuit of Style Points when one should be using more mundane tactics to actually win the game. Style Points, like you said, involves pulling tactics out of the rulebook and marveling at the suavity and debonairness of how they work. It's close cousin: The Charlie Brown moment.

Buzzsaw, or Buzz-saw: Killstack.

\section{C}

Caddie(s): Units lugging dismantled equipment behind the lead assault.

Campers: Infantry too busy with whatever to pass some TC.

Candygram: A Demolition Charge. 

Candygram for Mongo: Means, "the moving unit is placing the DC", and it is mandatory for the recipient to say "Mongo like candy" if the DC affects the target. 

Candy Man: Unit possessing a DC

Cannon: Non-MTR Gun.

Can Opener: Units or weapons that are particularly adept at eliminating tanks, or are attempting to be used as such. EXs: Nashorn, assault engineers with DC, or a conscript halfsquad (lamely) threatening CC.

Cappin' Mo'fo's: KIA'ing a unit or units with IFP/IFE.

Captain Darling/Percy: Any Brit 6 + 1 leader.

Captain Praxa: That preeminent German leader; any German 10-2+ leader.

Car Bomb: Ammo Truck detonated by fire attack.

Cardboard Pusher:  A player who doesn't know what he's doing.  Comes from "wood pusher" in the Chess idiom.  Different to a newbie, who has an excuse after all, a cardboard pusher would be someone who has played a lot and hasn't a clue.  Actually the chess world has other names for these that I (Trev Edwards) like:  Rabbit and Patzer are two I recall.

Care package: DC.

Carpet, Carpet Firegroup: Used to refer to a large multi-hex FG, usually used in the desert, where you have a FG of 6-8 squads in separate hexes. Or, a large, multi-hex firegroup, with no/few units stacked. See also Amoeba and Blob.

Cars: A DR of 6,6

Caught in the headlights:  A weak AFV that has failed to make its motion attempt after a large death dealing AFV has come into view.

Caught Stealing: Getting whacked while dashing.

Cav: Cavalry

CG: Campaign Game.

Chain Gun: ROF-3 Gun/SW on a Rate tear.

Chain-loaded: A Gun with a good ROF, either by design or good dice rolls.

Chemical Warfare: Player flatulence.

CINCHOME:  Wife/spouse/significant other. (Commander IN Chief-HOME)

Clank: The sound you make when one of your tanks Buttons Up.

Clayton: Fortify your hut. (ASL Name Slang)

Click: 1) The sound you make when one of your SW or Guns breaks. 2) Covered Arc Change.

Clip Fed: Refers to a large caliber, 1 ROF weapon that gets 3 or more shots in one fire phase, usually with great results.

CLP (copyright Dr. Rob): Cunning Little Plan - often said with an ironic lilt in the voice, in remembrance of dozens of previous CLP's that didn't last one turn before being shredded.

Clueless: Non-DM, broken Infantry adjacent to Concealed enemy Infantry, and thus unable to Rout away from impending CC.

Clutch Moment: A game-turning event.

Col. Klink:  Any 6+1 leader, preferably German.

Col. Klunk:  A dud.

Coming online: Fixing, assembling, or rallying a counter.

Commissar Denisova: That preeminent Russian leader; any 9-0 Commissar worth his salt.

Constellation: A position offering a number of low-odds opportunities (such as shots) yielding some good cumulative odds.

Consult the Book of Armaments: Look up something in the rulebook, esp.

Chapter H. (Monty Pythonism)

Cooked: A unit all but certain to be lost (related idiom: Stick a fork in them, they're done).

Counter Intelligence: Knocking over a concealed stack.

Country and Western stations only!: Rolled a 12 (a 6 repair dr becomes a relief!) (Preceded by an explicative)

Coward: Unit that skulks or uses Voluntary Break to avoid attack.

Cowereds: Those units whose IFT attack rolled doubles

Cowers Off: A 1 or 2 FP IFT shot that Cowers off the chart.

Crab crawl: The Platoon Movement "sleaze move"...

Crank: Start MP.

Crap: 1) Bad Equipment 2) Special Ammo

Creepers: Units moving concealed using AM and Advance.

Crit: Critical Hit, CH.

Critical Smoke: A Smoke TH DR of 1,1

Crush him like a bug: Overrun (or if you are David Longworth what he says to his opponents just before he wins).

Cup: Dice cup or plastic lid used for dice rolling.

\section{D}

Dance of Death: Armor-vs-armor closing engagement.

Dance through Resid: Using Infantry Bypass movement around +2/+3 TEM obstacles, risking +1/+2 Residual FP attacks.

Danger Mouse: DM.

DaMned: DM'ed.

Dashing Chaps: Infantry making a Dash move.

Dead Meat Marker: For those DM moments.

Dead Moose: DM'ed

Death by Half Squad: Aaron Cleavin's determination to deploy, deploy, deploy and then swarm, a focused variation on the Electric Football Attack.

Death Ray: Gun with very high TK number (EX: 17pdr or better)

Death Ray Stack: Killstack

Death Ride: Low-probability-of-survival move by vehicle/Cavalry/PRC.

Death Star, Death Star Stack: Killstack

Demon Squads: U.S. 1st Line 6-6-6 squad(s).

Dems da bones: Those are the dice.' Another way of saying you're S.O.L.'

Deuce: 1,1 on the dice.

Devil Squads: U.S. 1st Line 6-6-6 squad(s).

DiC: DC, as in someone's DiC is going to be in the wringer.

Diced: Defeated by an unusual run of dice.

Dice Gods: Supernatural forces who control the ebb and flow of luck in the game, whose perfidious whims we are at the mercy of.

Dig: Attempt entrenching.

Digs: A Foxhole dug during a scenario.

DIP: Element of a DIP Defense.

DIP Defense: Die-In-Place defensive plan.

Dfiring - Defensive firing (from VASL logfiles, rarely said in person).

Dice Audit: Invoked after a run of extremely good rolls by one's opponent.

Dim: As in, that guy is Dim, DM'ed.

Dimestore Cowboy: A SMC that hasn't done anything beneficial in over two turns (always pinned or broken, attracting fire but not beneficially modifying outward fire). A leader who never seems to pull his weight. See also Turd Ferguson.

Dog, Unbalanced Dog: 1) An unbalanced scenario. 2) Means, I'm losing and need to blame someone or something else besides my own blatant and all encompassing stupidity and incompetence.

Doggy Hex: Hex K9 on any board.

Doink/Clang: Sounds made when a To Kill DR is too high to affect anything- the sound of the shell ricocheting off the armor. Also known as "Bounce" or "Whiff".

Doomed: DM'ed

Door Knocker: ATG with poor TK\#.

Doormen: Units protecting Buzz-saws from upper-level encirclement.

Double time HARCH!: Going CX

Down: 1) As in 2 down 1, 2-1 attack 2) Broken

Drilled: SMC hit by a `1' Sniper attack.

Driveby, or doing a driveby: Firing MGs on the move at infantry.  Usually done while passing enemy units after getting Recalled (must get that free shot in, of course)

Duck Dice (plus synonyms): Dice with pictures (often a skull crossbones, but in the original case, a duck) in place of pips. It's VERY VERY IMPORTANT to know what is the "1" and what is the "6" on such dice. RIGHT, JAZZ?????

Ducky Dolan: Dodges or ducks an opponent at a tourney (ASL Name Slang)

Ducking: To make up lame excuses in order to not play an opponent at a

tourney.

Duh 'Cades (with a little streetwise inflection): Red Barricade CG.

Dumb: DM'ed

Dumb Mother-f*cker: DM'ed unit

Dutch Trucks: The fabled Doomed Battalions module, long in coming, as in "We want Dutch Trucks!"

\section{E}

Eat the Blast:  Fire a 'faust, 'schreck or baz from a building without paying the +2 DRM.

Elevator - Going Down:  Colored six on bog check in building

Electric Football Attack (copyright Steve Pleva) - Probably the best ASL jargon in existence. An attack that, like one's players in the old electric football game, starts out with everybody in the right place but is then turned into chaos, with people going hither and yon, willy and nilly.

El Jeffe:  9-2 or better leader

Elves: Hardworking little creatures who get ASL things done, such as the Vote Elves who tabulate the Best of the Year votes and the Map Elves who color the VASL maps.

End Game Rush: Last turn rush to fulfill the Victory Conditions, heedless of normal ASL sanity.

Even: Zero-modifier attack. E.g., 2 even, 2 +0 attack.

Evicting: Mopping-up.

Excited: HoB-capable infantry unit that passes a MC w/Snakes.

Eyes: Snake eyes, rolling ones on both dice.

\section{F}

Fair Shot: Needing an Original `5' or better on a TH DR.

Fankers: Tim Wilsonism for "flankers". You make one little typo, it goes down in history.

Fantastic: Fanatic.

Farmers:  Conscripts, originated by the pharmboy himself, Timbo Wilson.

Faust: Panzerfaust

Favorable TEM: In a firefight, having the better TEM.

Fearless: 1) Berserk unit 2) Unit conducting FPF.

Fedaykin: Russian 6-2-8 (Dune-ism)

Feed The Machine: Soak up fire by pushing units into oblivion with a greater goal in mind (like a killer OVR, the just-doable end game dash...).

Festung, the: A hedgehog or last-ditch point of resistance.

Final: Final fire.

Fine Red Mist: What's left after very high-firepower weapons fire upon units with a very good result. Or, a KIA result.

Finger Reconaissance: Knocking over your opponent's concealed stacks.  Accidentally, of course.

Fire-and-Forget OBA: Rocket OBA.

Fire Base Alpha: The hinge of your defense that is going to hold, or that you will feed until bled white.

Fire-dead: A final-fired or target-limited unit

Fire Phasers: Firing VTT with a guy that has a TK > 20.

Fire-pin: Send an AFV into the same hex as or in bypass beside enemy units to prevent them from being able to fire out. Also known as the Sleaze Freeze or simply Frozen.

First: First fire.

Fit it: Attempt to repair.

Fixed: Repaired SW/ordnance.

Fizzer: A malfed DC.

Flamer: FT, flamethrower.

Flame Strike: FT attack.

Flat: Zero-modifier attack. E.g., 2 even, 2 +0 attack

Flensing: from the VASL Map Cabal, the process of removing all colors except a few desired ones from a map. Derived from the Danish word for cutting blubber from a whale.

Flesh Wound, Just A - A wound severity dr that does not result in a KIA. From the Monty Python "Just a Flesh Wound" quote spoken by the Black Knight. (Monty Pythonism)

Flip: Break

Flood: A multi-unit move that absorbs/limits D1F to allow safer moves by other units.

Fly Boy: Air support.

Fodder: Units that are generally deemed as expendable. Conscripts.

Fog: Smoke

FM!:  Rolled a 2 on your radio contact attempt.

Forward Rout: Using Rout to close with the enemy.

Found the ammo: Repair a broken SW/Gun.

FRecon (pronounced "Free-Con"): When your opponent accidentally knocks over his own concealed stacks showing you what's there before you ceremoniously turn your head and pretend that you didn't see anything when in fact you saw everything worth seeing...

Freebie:  Your first MMC rally of your player turn.

Freeze: When a vehicle uses bypass movement in a hex to limit the defensive fire options of the enemy unit in the hex. Also known as "Sleaze Freeze" due to the possibly ahistoricity of the tactic.

From Beyond The Grave:  Residual FP from a now-dead unit (How does this happen?  12'd an FPF shot)

From Hell: an improbably successful or unstoppable unit.

\section{G}

Gack, Gacked: 1) A good attack foiled by a bad DR/dr. 2) A failed die roll e.g a 12 in CC. 3) A MMC/SMC KIA'd or whacked by a sniper.

Gamble: A decision to risk much on a few (or a single) DR/dr, forgoing conservative but less interesting options.

Gas Attack: Player flatulence.

Gerbil Werfer: Nahverteidigungswaffe.

Getting Stupid: Eschewing all good ASL sense in a last-ditch attempt to
make something good happen on the board. Running guys out in the open,
stack moving, whatever. Not often, but often enough, rewarded with
freakishly good luck, enabling one to turn the tide of battle.

Ghosts: A Dummy unit.

Gimp:  Wounded SMC.

Ginnard: Go outside for a smoke'. (ASL Name Slang)

Girls: A unit that performs remarkably poorly.

Give 'em the Splitter: Fire APCR/APDS.

Glass Jaw: An easily exploitable inherent weakness in an AFV. Little CC defense, an unarmored rear turret arc, etc.

Glory Move: Potentially strong move, but not likely to succeed.

Goalie: Unit protecting a Terrain/Exit VC area.

Goal Line: Hexes just in front of the enemy's exit or VC area; the line to be defended.

God: 10-3

God, Jr.: 10-2

God's OwnA very powerful or lucky unit.

Godzilla: Any FT'ing AFV

Go get her, Ray: Go Beserk, generally when such a result is far from favorable. From Ghostbusters.

Going Bush: Moving into woods hexes.

Going Postal:  A unit that just goes berserk.

Going To The Bullpen/The Lefthander: Switching dice when one's luck turns bad.

Goodies: Special ammo, WP, Smoke, sD, Gyrostabilizers, Schuerzen, or anything else that is considered "bonus" equipment.

Good Shot: One that should be good on a DR of `9' or less.

Grant's Tomb: Rubbled building Location where troops were crushed to death.

Grapeshot: Cannister ammo.

Gravediggers: Entrenching infantry.

Grease Spot:  Unit KIAed by an AFV Overrun.

Green Meanies: Same as Dutch Trucks, but for Armies of Oblivion. (Axis Minors)

Grill: PoW Interrogation

Grofaz: Grossten fur alle Zeiten (Greatest of All Time). Champion of ASLOK.

Grok (copyright Tom Repetti): As in "Groking the Essence". Its lineage dates from (iirc) Robert Heinlein's "Stranger in a Strange Land," but that's a story for Tom to tell ;).

Group hug (credit to JR Tracy): Failed deployment attempt.

Growing Lids: Concealment growth, gaining concealment.

Guerilla Warfare: Avoiding a straight up fight by means of street fighting, daisy chains, hedge hogging, etc. See also Hide-and-Go-Seek.

Guttersnipe: An opponent who's more interested in defeating you through sleazy tactics and obscure rules than just playing the damned game.

Gymnasts:  Romanian units.

\section{H}

Hail Mary shot: 1) LOOOONG range shot, e.g. anything beyond 20 hexes. 2) Pimp shot with low odds of having an effect but likely to yield a favorable result if successful.

Halfer, Halfie: Half-squad.

Handbag: DC.

Hand-to-Bolt Combat: CC attack on an AFV by Engineers and/or with ATMM or similar.

Happy: Infantry unit that passes a MC.

Happy happy, joy joy: Make a morale check or rally. From Ren and Stimpy.

Happy, Real: HoB-capable Infantry unit that passes a MC w/ Snakes.

Happy Hat: DM counter.

Hardware Store: Killstack

Hard/Soft Hindrance: Those which do/do-not affect firelanes with their hindrance DRM (Orchards/grain, for example).

Harped:  Leader/hero killed by a Sniper (as in: "Yeah, you harped him")

... Refers to the imagery of the spirit of the person playing a harp after death.

Heat of Pin: Rolling snakes on a PTC. Also for ESB, Bog, Stall.

Heat of Sniper: When you fire in your Advancing Fire Phase and get a pin check and your Sniper DR is "2" and he rolls a "2".

Heavy Hitter: ATG w/high TK\# or large-bore HE weapon.

Hedgehog: A way of defending that limits your opponent's ability to attack until they are at close or point-blank range. E.g., defending behind a treeline (as opposed to on the edge of it), defending behind the lip of a hill, defending the bottom of a gully the attacker must cross, etc.

Heisman: A SMC with a DC.  Usually a U.S. SMC (For those who don't follow U.S. College Football it is the annual trophy awarded to the "best" college football player.  The trophy is a bronze statue of a circa 1940's player running with a football under one arm and the other arm extended about to stiffarm a would-be tackler.)  I am sure other nationalities could come up with a more suitable name for an SMC with a DC.

Hello (or G'day): Attempting radio contact.

Hep, hep, hep (Credit to JR Tracy): Successful deployment attempt.

He's no fun, he fell right over: Broken, wounded or KIA SMC.  Obscure reference to Firesign Theatre comedy group (Wasn't it Dr. Martin Snow who always said he was Not Insane?).

He's not the messiah, he's a very naughty boy!: A 10-3 SS leader. (Monty Pythonism)

Hex of Death: A hex that, for some reason, instills instant deadly bad

karma on whoever's in it. Usually multiple units must die over the course of several player turns for a hex to gain HoD status, often in attempts to recover some crucial SW. See also Meat Grinder

Hide-and-go-seek: Giving the attacker the run-around with LOS and fire opportunities, i.e. skulking, concealing and re-concealing, HIP, daisy chains, etc., or just out rightly avoiding a straight up fight.

Hippy, Hipster: Hidden Initial Placement Unit

Hokey Pokey Panzer: A vehicle so pathetic no one pays it any mind. Worse than a tin can.

Hole: 1) Exploitable gap in a defense. 2) An oh-so-very hard to find loophole in the rules.

Holy Hand Grenade: Thrown DC. (Monty Pythonism)

Homer Simpson Moment: 1) One where just after you turned your turret facing to
the west, a HIP AT Gun shows up to your east, or run your best leader/squad
combo into an open street where you THOUGHT the LOS was blocked. Dohhhh!!!! 2) Making a mistake because you are oblivious to some detail that nullifies your entire plan, i.e. incomplete understanding or bad memory of the rules, i.e. ignorance. "Haha! My tank is now at level two! There goes your hulldown status!" "He's 12 hexes away and I'm behind a stone wall. He's fine." "Doh!"

Hopping on the Waaaambulance:  Whining about bad dice.

Horsie: Cavalry Horses.

Hunk-a-hunk a burnin' love: Turning a tank into a burning wreck, especially if the smoke favors your game play. See also Russian Smoke.

\section{I}

Idaho: Noun. A very baaaad place. (Mythical)

Ignorable: 1) A UK AFV you decide to treat as dead 2) A ? stack you decide to treat as a Dummy 3) DMed leaderless broken conscript halfsquad out of rally terrain.

I'm not quite dead!: A UK AFV or surviving wounded SMC. (Monty Pythonism)

In-Your-Face Rally: Self-Rally attempt on a unit that is Adjacent to the enemy and will probably die if the rally attempt fails.

"Is it a good plan?": Someone must immediately respond, "Oh, it's a great big plan!"

It's only a model: Said anytime someone says that a board is attractive. (Monty Pythonism)

\section{J}

Jack Move: Success in CC when swiftly followed by recovery of enemy SW.

Jailbreak: The enemy units holding up an advance are incapacitated in some way and it is time to move all friendly units forward, usually double-timed.

Janissary: Fanatic squad in position to Advance on armor for CCV.

Jedi mind-trick: Man you could write a book on these alone.  Everything from wondering out loud when your reinforcements come on board, to repeating the scenario title (That is why they call it panzer graveyard), to rolling dice, laughing when your opponent makes a move. Taking the game into the third dimension.

John Wayne: Any Hero, esp. American, who either (a) does something

particularly incredible and heroic (i.e., charges across the street and

kills a Tiger single-handedly); or (b) does something guaranteed to get him killed, usually for some cheesy game result (i.e., a Hero running up and down a Fire Lane to force a malfunction.), hence the verb, "to pull a John Wayne."

Joy Ride: 1) Solo AFV on the move in enemy territory 2) PRC traveling on an AFV 3) Driving a stolen AFV (very, very, very rare).

Junk: 1) Malfunctioned weapon. 2) Specialty ammo 3) Bad equipment. EX: Russian MMG suffering ammunition shortage. (Worse still: using conscripts to fire a captured Russian MMG w/ ammo shortage)

Junk mail: A DC that malfunctions (see Mail Bag).

Junk food: A DC that malfunctions (see Candygram).

JV, JV squad (short for Junior Varsity): 2nd line (or worse) units. Horribly outclassed by the majority of squads.  Make Russian 1st-liners enviable. Derogatory.

\section{K}

Kack: To KIA a SMC by sniper. See also Gack.

Kamikaze: 1) Tank-Hunter Hero 2) Cruddy AFV used to fire-pin/sleaze freeze a unit that could EASILY destroy it. 3) Misuse of trucks as offensive units. See also Selfless Acts of Heroism.

Killstack, Kill Stack, Kill-stack: A collection of units in one hex that are very powerful by design, and pack huge firepower and/or excellent leadership. Ex: 3x 658, 10-3 leader, 3x HMG

Kill Zone: Locations covered by effective defensive fires.

Killed Them: Said of a unit eliminated/CRed by a 6,6 Rally attempt DR.

Kirking a Roll:  Making a dramatic pause before rolling a Task Check or some similar non-critical roll (such as Searching, etc.)

Kiss the Dragon: Get fired on by a FT.

Kobolds: Russian 4-2-6's

Koenig!: 1 German SAN result.

Koresh Compound (copyright JR Tracy): The walled village on bd 43, often the spot where last-standers meet their end. I suppose it could also be called the Alamo, but I've never heard it.

Krauts: Germans.

\section{L}

Lacin' up the Nikes: The enemy unit(s) holding up an advance are incapacitated in some way and it is time to move all friendly units forward, usually double timed.

Land of Wind and Shadows, the:  Where your dead cardboard goes.

Last Words: The DFPh shots of an AFV on which a DC has been Placed.

Leaderhosen: When you kill a string of German leaders. AKA "Leader hosin'"

Left the gate open: Firing at a HD AFV behind a wall through a gated hexside, negating the HD status. More of a blunder on the part of the "HD" AFV's player than any tactical brilliance of the firer.

"Let's get the hell out of here!": Rout away from a dangerous situation. Must be said in a namby-pamby high-pitched British accent with a hint of fright. From Army of Darkness.

Lids: Concealment counter - In very common use (in Australia)

Lieutenant Gruber's Little Tank: Any 4 wheeled German Armored Car (from the comedy Allo Allo)

Likes it: Said of a unit that passes a MC.

Limies: British.

Lonely: Unit engaged by the enemy and without adequate support.

LSOB: Lucky SOB, as in, "You LSOB" (Pronunciation: Less-Oh-Bee)

Lucky: 1) A unit unscathed by (many) strong attack(s) 2) A unit selected by RS for some attack effect.

Lug: Carry, e.g. Lug this MMG.

Lurkers: Units set-up in Cellar locations

\section{M}

Magic Moment: A memorable game event in your favor.

Mail Bag: A DC

Mailman, Mailmen: DC-toting unit(s).

Malf'd: A SW or gun/vehicular gun that is inoperable due to a malfunction.

Malf Check: The DR after determining a declared shot's LOS is blocked.

Management Consultant: POW unit used to Deploy squads.

Manic Depressive: HoB Surrender result.

Mareenie you die!: What Jap player yells periodically when playing vs.

USMC (Or, more appropriately and even less PC, "Maleenie you die!")

Mayberry: Board 10 village

McFly!: Said repeatedly (with the headknocking hand gesture) after a stupid move. From Back to the Future.

Meat: Horse counter destroyed by combat.

Meat Grinder: Situation or location that has claimed many many CVP. Usually a Victory Location building or a particularly nasty CC, where unit after unit after unit is eliminated. Common in city scenarios and Red Barricades. See also Hex of Death, Alamo, and Koresh Compound.

Melt the Barrel: Firing one's Gun as much as possible, including Sustained or Intensive Fire, as it is that unit's job in life to cause casualties and then die.

Men in Black, MIB: Black SS units/counters.

Metagaming: Using your troops or equipment in such a way that, in reality, it
historically would never have been used. This is required to win in ASL.  Ex:
90\% of sleazes are this.

Minigun: HMG on a rate tear.

Mini-snipe: What you get when you roll a 2 on a sniper dr. Also known as a baby sniper or a "warm" result, where a "1" on a sniper dr is "hot".

Miracle Rally: The first rally of your Player Turn. See also Super Special Self Rally.

Miracle Worker: Leader who Rallies MMC despite unlikely odds.

Mission Killed/Dead: Units not actually eliminated, but considered out of play with regards to VCs (or capability). E.g., AFVs immobilized behind LOS-blocking terrain with incredibly limited fields of fire.

Mods: Modifiers

Money Shot: Shot with best potential, going into a DFPh or PFPh.

Mollies: Molotov cocktails.

Mortar Madness: That thing that happens only in RB when there is a dozen or so mortars (of either side and various calibers) set-up on the roofs and blazing away...

Motivational Speaker: A Commissar.

Mr. Big: A 9-2 or better leader.

Mr. Joy: A Commissar.

Murphed:  Hero creation, inspired by Audie Murphy (as in:  "I got that

squad shot up, but I HOB'd and got Murphed")

Mystery: 1) An apparently silly move by the opposing player 2) A ? stack.

\section{N}

Naked: TEM-disadvantaged unit in a firefight.

Nancy-Boys (copyright JR Tracy, I think): For squads/HS that perform very poorly.

Needing a small number: Rolling for a TH attempt without figuring up the modifiers unless the DR is sufficiently low enough to have a chance of hitting and warrant actually doing the math. Usually a pimp shot or fire to acquire.

Negative Waves:  Malfing MA.

Newbie: Noun. Pejorative expression for a new (or bad) player.

New Jersey: Noun. A very baaaad place.

Noogiewoofer: The Nahverteidigungswaffe sN smoke dispenser.

`No Roll': Declared to void an unsettled DR (owing to a die bounced from the dice glass, usually).

NRBH: No Rule Book Handy. Mentioned when answering a rules question sans rulebook on the ASLML.

\section{O}

Off the Charts: Any shot of more FP or penetration than is given on the charts. E.g., A 40 FP attack or 21 penetration gun that scores a CH.

Off the Table: 1) A 1 or 2 FP IFT shot that Cowers off the chart. 2) IFT shot w/enough `+' DRM to be worse than a 1-flat.

One-check: 1MC

Once More, With Feeling:  A ROF shot.

Opera: What your RTO hears when you miss your Radio Contact DR.

Out of Phase: A minor violation of the ASOP

\section{P}

Paint: Residual Firepower (idiom:  `paint with Resid')

Paint Round: A Dud on a TK attempt. From the movie "Kelly's Heroes".

Pansies: Infantry that fail a PAATC.

Panzerblitz Assault: VBM freeze followed by PB/TPB AFPh attack followed by CC attack.

Paper Tiger: A tank (esp. Tiger) that completely fails to do anything useful before being eliminated. Or, an AFV with a large caliber gun but very little armor (e.g. a Nashorn).

Parade: 1) Leader-led Infantry platoon stack-moving in the open. 2) Two or more vehicles in the CA of a high-ROF weapon.

Parking Lot: Two or more Stopped AFV in the CA of a high-ROF ATG.

Parting Shot: BFF shot by a vehicle under Recall.

Patsy:  PAATC (Pre-AFV Attack Task Check).

Peek-a-boo!: Stripping concealment or HIP, then firing.

"Perfect execution of an awful plan.": Similar to the Electric Football Attack.

Perrogies: Polish Armor

Phaser Stack: Killstack.

Phone Sex: Field Phone Contact DR of 1,1.

Phoop or phump: Mortar, the sound made by.

PIAT: Pronounced "PEE-yot". The PIAT.

Pikachu, I choose you!: Referring to Tank Hunter Heroes, especially Japanese. Credit goes to JR Tracy.

PIKN: Personal intoxication kindling number.

Pimp Shot: Any low-odds shot that succeeds in breaking or doing worse damage to the target, eg 1+2, 2+3, etc.

Pinata:  AFV in a streetfighting location.

Ping: 1) Fire to acquire 2) Bounce an AFV TK shot.

Pinhead, Pinnies, Pinny: A pinned unit.

Pip: the one dot on a six-sided die.

Pipper: An acquisition marker.

Pissed: 1) HoB MC/Rally of a Broken unit. 2) Berserk.

Place Resi: To place Residual counter after attack.

Plan B:  Next move after a particularly ineffective fire attack or the KIA of a moving unit.

Plentiful Spare Barrels: A Malfunctioned MMG/HMG Repaired at the first opportunity.

Plevanator: Rolled you up (ASL Name Slang)

PMC: Personal Morale Check. Your resolve as a player not to give up or get discouraged after a setback.

Pokey Perry: Play slow. (ASL Name Slang)

Poof: The sound you make when you bring down OBA smoke (7 hexes of white powdery substance). Could also be used for any French SMC.

Poor Dumb Bastard: A unit fated to be eliminated with no means of preventing it's own demise, e.g. DC placed in their hex, FT tank next door, etc.

Pop: Turn an AFV into a Burning Wreck.

Pop/Blow Smoke: Use a vehicular smoke discharger.

Popped a Wheelie:  Snake eyes on a trannie check.

Popular: A high-morale SMC that pins/breaks/reduces his own units via LLTC/LLMC failures.

Potatograd: Any East Front town being fought over by the Germans and Russians. Refers to the village in the 1942/1944 East Front Campaign playtests (you'll see what I mean someday).

Probe Fortifications: Use of a Dummy unit (on point) to find HIP.

Programmed Move: A mandatory Rout (or other move) offers no options.

Puddle: Residual Firepower

Pulling Guard: (American Football reference) A unit that moves closer to cut the SFF range of the opponent while friendly units run on by.

Purple Germans: Original color of the German counters in KGP.

Purple People Eater: KGP German unit(s).

Pustule: Conscript squad.

Pustulize: The process of degrading a unit into conscripts. See also Scriptification.

Pyromaniacs: MOL-capable Infantry.

\section{Q}

Quartermaster: Friendly (or enemy) deliverer of a Recoverable SW.

\section{R}

Rally Machine: Commissar (or high negative DRM Leader) used (with high probability) to put troops back into the fight, fast.

Rally or Die: When a unit needs an 11 or less to rally, or a commissar is involved.

Ralphing:  Multiple ROF from the same MG/Gun.

Rambo: A Hero or a Heroic Leader.

Ranging Ping: AFPh TH attempt with little or no hope of producing an effect [EXC: acq.] Pittsburgh slang for this is: "Fire to Acquire"

Rate: rate of fire.

Razor Blades:  Wire.

RBI: Victory Points already exited. From baseball term "runs batted in".

Reality: The only one that matters is defined by ASLRB. To be specific it is the version 2 of that reality that counts. The other reality, where players reside (well most of them), is sometimes used as base [illegally] for interpreting the rules in a favorable way.

Realtor: A MMC moving to take uncontested control of buildings.

Recon by Fire: Fire at an empty hex in an attempt to find HIP units.

Recon by Rout: Using Rout in Night scenarios to strip Cloaking/ Concealment; also possible (but fatal) by day.

Red Barbecue: Red Barricades CG

Red Smear: KIAed unit.

Repetti: Getting your AT Gun hauled off the board by your opponent for Victory Points. (ASL Name Slang)

Resi: Residual counter

Resid: Residual firepower.

Residue: Residual firepower.

Resurrection: Full recovery of a previously ignored UK AFV.

Revolving door: An efficient rout path setup.  Units break, rout back, get rallied, go forward again, break, rout, rally... Especially effective and common with American units.

Rhodes Scholars: A unit used to draw fire.

Ringpiece shot:  A TH/TK attack against the rear target facing on an AFV.

Ring the Bell: Get a SHOCK result on an AFV.

Rrrroaf (much rolling of the 'r'):  ROF, pronounced as a word by our

Continental friends.

Roll-back: Agree to a minor violation of A.2.

Roll, Get Rolled: When your offense/defense gets turned into a giant rout. Similar to Roll Over.

Rolling Crap: Bad vehicles - similar to Tin Cans

Roll Over: 1) Fail morale check. 2) Decimate your opponent.

Roman Candle: 1) An Italian tin can. 2) A burning wreck.

Ronson: 1) FT (also Flamer) 2) An AFV (usu. earlier US tanks) with red crew survival numbers.

Roofers: (German) HS set up on an accessible rooftop location to deny HIP and concealment for enemy units set-up on rooftops.

Rookies: Conscripts/Inexperienced/Greenies

Rototiller: 150mm or larger OBA/Rocket OBA (it just tears around creating shellholes).

Roving Pillbox: A lauding term for a practically unkillable tank.

RTO: Leader with a Radio.

Rules Bitch: The person with the rulebook in their lap who has the honor of looking up the rules because they have the book.  Both a blessing and a curse, as its annoying to be the one doing it but you can research your strategy without having to ask in advance.  E.g., you can double-check rules on bogging in the stream without informing your opponent you're considering it. (But you counter the rules bitcher by being the guy with the rulebook, looking up the rule, and regardless of how the rule actually reads, lying about it so the rules decision always ends up with you being right. Least that's how I've always done it, Youse can't since he doesn't look in the rulebook, and Perry, well no one ever rules bitches to Perry when they play him (kinda like questioning Bob McNamara second hand ain't it?))

Rules Dive: A pause to check something in the rules.

Rules Lawyer: One who goes to great lengths to find the right interpretation to a rules dispute. "Right" being in the eye of the beholder.

Run Away!: Said while routing. (Monty Pythonism)

Run Interference: 1) Use expendable units to soak up D1F or distract your opponent while you move up the important units or bulk of your of stuff. 2) Send units on (suicide) missions into your opponent's flanks or rear to wreak havoc (cut rout paths, re-DM brokies, slow down movement). More of a nuisance than an actual tactic, though it can take the steam out of an attack if your opponent doesn't handle it correctly.

Run like girls:  As in, "my guys are going to self-break and run like girls to the rear." 

Russian Smoke: A burning wreck.

RV: AFV (or any off-road vehicle).

\section{S}

Sabot: APDS.

Sad: Broken.

Sardaukar: Referring to the German 838's similarity to the Imperial Sardaukar from Frank Herbert's Dune saga as the elitist of the elite. (Dune-ism)

Schilling: Spit your tobacco juice into your dice cup (ASL Name Slang)

Schindler's Rounds: A dud, usually associated with rolling a 12 TK with a PF or PSK.

Schnubblewerfer: The Nahverteidigungswaffe sN smoke dispenser.

Scoped: 1) A Location covered by fire on a non-obvious LOS. 2) Boresighted or preregistered hex.

Scout: 1) HS used for recon. 2) Mobile AFV with no functioning weapons.

Screaming alfas: Infantry KIA'd by flame attack.  Reference to Class A fires (Class A fires leave ash; Class B is petroleum; Class C is electrical).

Screen: Friendly unit in the hex and outside a friendly pillbox.

Screwed: 1) DM'ed units that will either be eliminated for failure to rout or surrender. 2) Lightly or un-armored AFV staring down the barrel of a biiiig gun.

Scriptification: Process of declining squad quality.

Selfless acts of heroism: Using tin cans, halftracks or armored cars to fire-pin an enemy AFV or stack by going into bypass beside it or entering it's hex. Also known as sleaze freeze.

Senior Moment: Some senseless move or blunder.

Septics: As in Septic Tanks; Yanks. (Don't Ask, Aussie nickname for American units)

Sewer Rats: Sewer-moving units.

Shelling: Momentarily blinding your opponent during a crucial moment (with your dome) (ASL Name Slang)

She Who Must Be Obeyed: One's wife or Significant Other whose permission is required to attend an ASL gathering. See also CINCHOME.

Shooting Blanks: Infantry shot with no effect or dud ordnance.

Short Game: Fun, reckless play (idiom:  Let's go for the short game).

Shot Back: The attack back by enemy engaged but not affected.

Shotgun: Canister-firing gun.

Shreck: Panzerschreck

Sielski: Fondle your dogs (ASL Name Slang)

Singed: Effected by Backblast.

Sixth sense shot: The idiosyncrasy of ASL where units can fire at enemy units where the LOS is questionable, so that they will unsuccessfully fire at units they can't see.  Usually results in a squad unleashing on a small grove of trees that's blocking LOS. "The sergeant sensed enemy units to the north..."

Skulk: On your MPh, Assault Moving backward out of enemy LOS to eliminate defensive fire opportunities, then Advancing back to the front line to prepare for your own defensive fire.

Sleep!: As in the hypnotic chant invoked to make sure your opponent's

Sniper does not activate, or "Wake up!"

Sleeping: A Sniper who misses.

Sling Fire: TH attempt by a non-Stopped AFV.

Sling Shot: 1) TH attempt by a non-Stopped AFV. 2) A PIAT

Slink: An Assault Move or Advance.

Smack: Hit target.

Smoke at the Feet: The Hindrance for firing down from Level 2 when smoke has been placed at Ground Level.

Smoke in the Eye: The Hindrance for fire from a SMOKED Location.

Smoke-maker: 1) A SMOKE-capable unit. 2) Armor likely to end the scenario as a Burning Wreck.

Smoke Phase (SPh): 1) First section of PFPh or DFPh where SMOKE is fired. 2) Phase taken before the Rally Phase to go have a cigarette. See also UPh (Urination Phase)

Smokie the Bear: Unit carrying a FT.

Smokin' Shoes!: A large caliber hit resulting in KIA. Refers to Three Stooges when they were shot from 10 feet away by a coastal defense gun.

Smooth Move: 1) An admirably good move by the opposing player. 2) A blunder on your part.

Snake eyes, snakes: Rolling 1's on both six-sided dice.

Snap: To fail a MC (to break).

Sneffle-boffer: The Nahverteidigungswaffe sN smoke dispenser.

Sniped him: Unit selected as sniper target (also Whacked)

Sniper bait: 1) A good or important leader out on his own, far away from any other unit.  Has "shoot me," written in a large sign on his back. 2) Any shot where the odds of it activating the enemy sniper are roughly equal to, or better than, the odds of it accomplishing anything useful.  Usage:  "Oh, wait, I forgot to include the +1 for CX.  That makes it a 2+3, and it won't even DM him... Ah, forget it, that would just be sniper bait." 3) The term might also be used for a unit INTENTIONALLY put near a Killstack, to soak up sniper activations that might otherwise disrupt the kill stack's functioning, but "sniper bait" is NOT properly used to refer to a good or important leader who is accidentally left vulnerable to a sniper.  The proper ASL term for that is "really dumb of me", as I (John Brock) know from my almost constant usage of it in this context. 4) A DR as likely to hit SAN as to get an effect. 5) A low-value unit positioned to absorb a Sniper attack (and thereby save a better unit).

SnitzelShredders: The Nahverteidigungswaffe sN smoke dispenser.

Snoogiewoofer: The Nahverteidigungswaffe sN smoke dispenser.

Snub: To kill, esp. a leader

Snub gun: A "*" gun, i.e. short-barrel. E.g., "What does that Mark IV have?" "A 75 snub gun." (a 75* MA)

Socked-in: SMOKED firer.

Sorry: Broken.

Special bullets: Special ammunition.

Specialist: SMC (8-0, typically) employed as a FT or DC operator.

Speed Bump: Unit designated to slow down the enemy and/or provide enough of a threat so that he can't move in stacks. This is often countered by the Track Meet or Sleaze Freeze. Speed Bump units are often considered expendable.

Spike the tank: Place a DC on an AFV.

Spike the barrel: Deliberate SW/Gun elimination.

Splash, splash counter: Residual firepower.

Spousal Task Check: Process of checking with She Who Must Be Obeyed.

Spuddy: A gold statue of a spud. Given in recognition of "Humor above and beyond the call of duty in the face of the enemy". (An annual award given on the ASLML for humorous posts.)

Squad Destiny: A MMC or killstack destined for greatness.

Squeaky: A close LOS.

SS Auto Rally Phase: Rallying SS that are not DM.

Steaming Perrogies: Knocked out Polish "armor".

Stepping Out/Outside: Avoiding Backblast by paying +2 during the AFPh.

Steve McQueen: SMC motorcyclist.

Stolen: Captured SW/Ordnance.

Straight: Zero-modifier attack. E.g., 2+0 attack, a 2 straight attack. See also Up and Down.

Striped:  Step-reduced, as in an IJA squad flipped to its striped side.

Studs: Infantry that pass a PAATC.

Stuff: Special ammo. As in, "rolling for stuff."

Stuffed: KIA or Destroyed

Stupid Americans!: Said every time you break and ELR your Amis, get eliminated for failure to rout, get captured, or get one of your AFVs killed because you forgot to play the Americans the way they are supposed to be played!

Stupid Road Tricks: From the VASL Map Cabal, the terrain change feature coming up in VASL v4 that allows one to remove all roads on a board except for certain user-defined sections.

Stupid Signs: For any assorted malfunction/ammo out sign attached to an AFV.  "Hey, Fritz!  Let's go attack that Panther over there!  It has a MA Malf sign up!!!"

Super Special Self-Rally: The first MMC rally attempt at the beginning of the turn. See also Miracle Rally.

Surprise: 1) Any unexpected event. 2) A HIP unit/stack. 3) A mid-game realization of some SSR or VC.

Swarm: A multi-unit move that absorbs/limits D1F to allow safer moves by other units.

Swing: Change CA/VCA

\section{T}

Tactical Genius: Clever results achieved via a good run of dice.

Target: A HS used as a scout to draw fire

Target Rich Environment: 1) Unit/Weapon with a long menu of shot opportunities. 2) Many, many units that would make suitable targets.

Team Acrimony: Pleasantly informing your teammate that he royally screwed up.

Teleport: The Platoon Movement "sleaze move"...

Teleported: SMC generated shortly after being eliminated elsewhere.

Temps: Enemy prisoners used to entrench or clear roadblocks/minefields.

That Most Dangerous of All Animals: A berserk conscript half squad.

(T)he {insert optional curse here} Daniel Boone: from Red Storm Rising, a squad with a deadly accurate mortar.

They don't like it up 'em, Cap'n Mainwaring!: Upon entering HtH combat, preferably when using Brits. (Dad's Army, Corporal Jones)

Through the 5 hole: An otherwise devastating shot that missed or had no effect.

Throwing Rocks: A Dean McGinleyism for "using AP shells as HE".

Thin Red Mist, the: What's left after very high-firepower weapons fire upon units with a very good result, i.e. a KIA result

Those Valiant Defenders of the Motherland: Broken Russian conscript half squads.

Threw a track, threw a tread: Failed ESB attempt

Tiger Woods:  Any Woods location with an AFV-created trail break.

Tin Can: Derogatory term for a bad tank.

Tired: CX'ed

Toast: A unit all but certain to be lost.

Tome, the: The ASLRB, suggesting its canonical and lofty

position among ASL players.

Torchers: FT-toting units and stay-behind Russians setting fire to buildings.

Toy: 1) A SW or Gun. 2) Special equipment/ammo on an AFV.

Toy Chest: Those halftracks that can be scrounged for their multiple MMG's and HMG's.

Track Meet: When you line up your entire force and move them individually (usually CX) in an attempt to overwhelm the enemy. Minimizes the opponent's chances of doing serious damage.

Tractor Beam: Used by AFV to Push AFV/Wrecks in their Location but out of LOS owing to some obstacle both are Bypassing.

Traffic: Difficulty of moving many units in a congested area.

Traffic Jam: Having to go around or pay extra movement to get past a congested area.

Transmission Check, Trannie Check: Mechanical Reliability DR.

Trap: Some element of a setup designed to surprise the opponent.

Treeline: The outside, easily visible edge of a clump of forest.

Trey: Three (as in, rolled a trey)

Trog (troglodyte): IFT user who has yet to see the light.

Troll: Any unit in a cave.

Tune in Tokyo: Radio Contact DR for the Japanese.

Turd Ferguson: The honorary name of a 6+1 or perpetually broken leader.

Turret Sweep: When an AFV changes TCA while moving thereby forcing riders to Bail Out.

Tweeters: Snake eyes.

\section{U}

Unhelpful: Results of a poor dice throw or a poor run of dice.

Unimpressed: Survivor of a strong attack.

Unprotected Sex: A Human Wave/Banzai conducted across unhindered Open

Ground.

Up: 1) As in 2 up 1, 2+1 attack. 2) A rallied unit.

UPh, Urination Phase: Necessary inter-phase activity (insert as needed
into ASOP.) There is also the NPh (nicotine phase, for smokers), FPh (food phase), and BPh (beer/booze phase).
UPS Man: Friendly (or enemy) deliverer of a Recoverable SW.

\section{V}

Vader: SS 10-3

Veteran: Visibly worn game piece, such as a weathered 8-1 SMC.

Viking funeral:  Burning AFV, especially with AL trapped inside.

Virtual Hero: One generated and eliminated before taking any action (often in the same ROF tear).

Voice Control Dice: Dice that apparently answer calls for a 1,1 or 6,6 roll.

Volley Fire!: Multi-hex fire group.

Volunteer: 1) A halfsquad (or rarely a Squad or SMC) that is given the job of leading the attack by crossing open ground and sometimes involves runs into an enemy stack to strip concealment. They are often broken or KIA'd in the process. Falls under the category of "Acceptable Losses". 2) A SMC created by combat effects.

Vulnerable: Infantry subject to sure capture/elimination if they break.

\section{W}

Waffles:  Belgian troops.

Walking TEM: A `-2' (or better) leader stack-moving w/Infantry to assist their MCs vs any D1F.

Wall of Resid: A barrier of residual firepower across an attack axis.

War Crimes!:  Somebody just invoked No Quarter.

War Criminals: SS units/counters.

Wavers, aka Wave-men: Units participating in a Human Wave, or multihex Banzai charge. Also Surfers or Ronin.

Weenie roast: Successful FT attack.  Brewed-up AFV with no surviving PRC.

Whacked: Unit selected as sniper target.

Where's the beef?: Said to your HMG that never gets rate.

Weapons Dump: A concentration of unpossessed SW/Guns.

Welcoming Committee: Defenders with Attackers in their kill zones.

Willie Pete/Peter: WP.

Wimp: Unit that fails some easy mission.

Windage:  The weather DR at the start of a turn. 

Wind Sniper: Rolling the SAN on a Wind Change DR.

Winged: Wounded SMC.

Wing it: Handle a rules question without making a rules dive.

Winner: Unit selected by a Random Selection for an attack effect.

Woofers: Boxcars.

Woosh: FT

Woossie: A unit that breaks to a low odds attack.

WTC/STC/SOTC:  Wife Task Check/Spousal Task Check/Significant Other Task Check.  Task check (usually accompanied by positive DRM) that must be passed before:  1) playing a game; 2) hosting a game; 3) attending a tournament; 4) buying ASL stuff.

\section{X}

X'ed: 1) Malfunctioned (Gun/SW flipped to the `X' side). 2) Disabled/ removed
(X\# instead of a B\#)

\section{Y}

YAHIRA: Yet Another Hopelessly Inconsistent Reality Argument.

Yahtzee: 1) From the game of the same name, a random selection DR where multiple dice come up the same number. 2) A RS DR that selects more than one unit.

Yard Sale:  A pile of unpossessed support weapons, their original owners having departed to The Land of Wind and Shadows.

Yella: Broken unit

Youse: ASL unit of whining (copyright Tom Repetti). Often measured in milliyouse, but often regular Youse will do.

Youse-meter: The device which measures Youse.

\section{Z}

Zaitsev: A hyper-Sniper, esp. Russian.

Zerkers, Zerkoids, Zerks, Zerkie: One or more Berserk units.

Zids: Residual Firepower.

Zippo:  FT, usually the SW variety.

Zoomie: Air support.

\end{document}
